Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/background.tex
beep
Abstraction notation in background now all nicely partitioned into definitions

We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme. Consequently, this mapping induces an abstract MDP. Let:$M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.

% States
The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$. More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
\begin{equation}
\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
\end{equation}

Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition. We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.

% Reward
The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
\end{equation}
\dnote{Need to change the subscript here.}
% zzz g in phi(s) seems like a type error, no?

% Transition
The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
\end{equation}
\noindent where $
s, s' \in \mathcal{S}_A
$.

We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
\begin{equation}
\left(\sum_{s \in \mathcal{S}_G} \omega(s)\right) = 1,\hspace{6mm} \forall_{s \in \mathcal{S}_G} \omega(s) \in [0,1]
\end{equation}
\enote{This ins't right -- should be a prob distribution over ground states of a \textit{single} abstract state -- not all ground states.}

>>>>

\bdefn{$M_G$, $M_A$}
We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme. Consequently, this mapping induces an abstract MDP. Let $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.
\edefn

% States
\bdefn{$\mcS_A$, $\phi$}
The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$. More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
\begin{equation}
\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
\end{equation}
\edefn

\bdefn{$G$}
Given a $\phi$, each ground state has associated with it the ground states with which it is aggregated. Similarly, each abstract state has its constituent ground states. We let $G$ be the function that retrieves these states:
\begin{equation}
G(s)=
\begin{cases}
\{g \in \mcS_G \mid \phi(g) = \phi(s) \}& s \in \mcS_G\\
\{g \in \mcS_G \mid \phi(g)=s \}& s \in \mcS_A
\end{cases}
\end{equation}
\edefn

The abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition. We make no assumptions about the weighting scheme, except that for each abstract state, the weighting is a convex combination across all ground states.

\bdefn{$\omega(s)$}
We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
\begin{equation}
\forall s \in \mcS_G \left(\sum_{s \in G(s)} \omega(s)\right) = 1 \texttt{ and }\hspace{6mm}  \omega(s) \in [0,1]
\end{equation}
\edefn

% Reward
\bdefn{$\mcR_A$}
The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{R}_A(s,a) = \sum_{g \in G(s)} \mathcal{R}_G(g,a) \omega(g) .
\end{equation}
\edefn

% Transition
\bdefn{$\mcT_A$}
The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{T}_A(s,a,s') = \sum_{g \in G(s)} \sum_{g' \in G(s')} \mathcal{T}_G(g,a,g') \omega(g),
\end{equation}
\edefn

### 2016-02-03 paper/theory_results.tex
Abstraction notation in background now all nicely partitioned into definitions

% Intro to approx state abstraction results.
Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods. In particular, we demonstrate that abstractions based on $Q^*$ similarity (\ref{sec:Q*}), model similarity (\ref{sec:model}), and similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.

@@

\begin{defn}
To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
\begin{equation}
V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
\end{equation}
\end{defn}

@@

\begin{defn}
Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
\end{defn}

\begin{defn}
Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
\end{defn}

>>>>

% Intro to approx state abstraction results.
Here, we introduce our formal method for analyzing approximate state abstraction, including results bounding the error associated with these abstraction methods. In particular, we demonstrate that abstractions based on approximate $Q^*$ similarity (\ref{sec:Q*}), approximate model similarity (\ref{sec:model}), and approximate similarity between distributions over $Q^*$, for both Boltzmann (\ref{sec:boltz}) and multinomial (\ref{sec:mult}) distributions, induce abstract \acp{MDP} for which the optimal policy has bounded error in the ground MDP.

@@

\bdefn{$\pi_A^*$}
To evaluate a the optimal abstractpolicy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
\begin{equation}
V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
\end{equation}
\edefn

@@

\bdefn{$Q_G$, $V_G$}
Let $Q_G: \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G: \mathcal{S}_G \rightarrow \mathbb{R}$ denote the optimal Q and optimal value functions in the ground \ac{MDP}.
\edefn

\bdefn{$Q_A$, $V_A$}
Let $Q_A: \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A: \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the optimal Q and optimal value functions in the abstract \ac{MDP}.
\edefn
